---
title: "eds222-final-project"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

**Final Project**

*Data*
- Source(s)?
- Completeness?
- Processing?

*Explore*
- Visualize
- Summarize
- Hypothesize

*Analysis*
- Method?
- Implementation?
- Diagnostics?

What is my hypothesis.

Determine the P-value.

Spend a lot of time on the methods, explain research question, objective, where the data is from. Add citations where applicable. Does the data satisfy the needs of the analysis?  EX: “ I need to do another test because my results aren’t robust enough” 

Linear or logistic regression based on hypothesis and data.

Determine/explain what the indexes are representative of.

Tidy the data, make it longer and compare state by region and make it a categorical variable for a logistic regression: “How likely is it that a state is in a  given region based on the values for fert/pest use”. Or I could compare a state to the national average. 

Remove yield consideration from research question: it is already assumed that pest/fert affects yields.

Potential OVB: is total area represented?  because that affects yield.


**Outline**

*Intro*
- Introduction
- Data summary & citation
- Research question & objective

*Setup*
- Load packages
- Read in data

*Data preparation*
- Remove extraneous rows/columns
- Pivot longer
- Add region column

*Data exploration & processing*
- Visualize data
- Find the p-value
- Hypo statements
- Determine methods

*Analysis*




```{r}
library(tidyverse)
library(here)
library(readxl)

crop_output <- read_excel(here("data/new_crop_output_state.xls"))


pesticide <- read_excel(here("data/pesticide_consumption_state.xls"))
labor <- read_csv(here("data/labor_etc.csv"))

```


```{r}
fertilizer <- read_excel(here("data/fertilizer_consumption_state.xls"), skip = 5, range = "A6:AW53")

fertilizer_clean <- fertilizer[rowSums(is.na(fertilizer)) < ncol(fertilizer), ]
```



